Robust-Adaptive Control of Linear Systems:\\ beyond Quadratic Costs

### 2020-10-13 paper/main.tex
Fix typos

\paragraph{Outline}
In \Cref{sec:proof}, we provide a proof for every novel result introduced in this paper. \Cref{sec:attachments} describes the attached video files and source code. \Cref{sec:experimental-setting} provides additional details on our experiments. \Cref{sec:tight-polytope} gives a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}. Finally, \Cref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.

@@

By \Cref{lem:dynamics-est-bound} and the above, the sequence $(A_N)_{N}$ converges to $A(\theta)$ in Frobenius norm. Thus, 
$$M_n \eqdef \begin{bmatrix}
A_N^\transp P + P A_N^\transp + Q_0 & P|D|  \\
|D|^\transp P & -\rho I_r \\
\end{bmatrix}\text{ also converges to } M\eqdef\begin{bmatrix}
A(\theta)^\transp P + P A(\theta)^\transp + Q_0 & P|D|  \\
|D|^\transp P & -\rho I_r \\
\end{bmatrix},$$ which is assumed to be negative definite.

@@

\section{Description of attached files}
\label{sec:attachments}

\paragraph{Videos}
The \texttt{video} folder contains videos comparing trajectories of the oracle planner and \Cref{alg:full}. The oracle planner has access to the true dynamics and follows aggressive trajectories that nearly saturate the collision constraints. In contrast, the \Cref{alg:full} produces more conservative trajectories. In the obstacle experiment, we show the confidence ellipsoid over $\theta = (\theta_x,\theta_y)$ in the right panel. In the driving experiment, we show the multi-model rejection and robust selection procedure through the display of several trajectory hulls for all possible destinations of the observed vehicles.

\paragraph{Source code}
The attached \texttt{code} directory contains an implementation of \Cref{alg:full}. The \texttt{README.md} file relates the algorithmic steps of this paper to their location in the source code, and contains instructions to reproduce our experimental results.

>>>>

\paragraph{Outline}
In \Cref{sec:proof}, we provide a proof for every novel result introduced in this paper. \Cref{sec:experimental-setting} provides additional details on our experiments. \Cref{sec:tight-polytope} gives a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}. Finally, \Cref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.

@@

By \Cref{lem:dynamics-est-bound} and the above, the sequence $(A_N)_{N}$ converges to $A(\theta)$ in Frobenius norm. Thus, 
$$M_n \eqdef \begin{bmatrix}
A_N^\transp P + P A_N + Q_0 & P|D|  \\
|D|^\transp P & -\rho I_r \\
\end{bmatrix}\text{ also converges to } M\eqdef\begin{bmatrix}
A(\theta)^\transp P + P A(\theta) + Q_0 & P|D|  \\
|D|^\transp P & -\rho I_r \\
\end{bmatrix},$$ which is assumed to be negative definite.

@@
